---
title: "Does Karsa make RNG better?"
author: "SkySpiriT"
date: "2018年6月23日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Karsa and Mlxg

In world of LOL , there is a chinese team: RNG .

It's one of best team in the world.

There is a taiwanese palyer :Karsa.

In this year, go to RNG from taiwanese team FW as their new Jungler.(Jungler is a role position in LOL)

But there is a question.

RNG still have a original Jungler :Mlxg.

There is a fighting between Mlxg& Karsa's fans: Which one is better?

It's also I confuse about.

So,let's survey!

## Get RNG race information

I get the race in April to June of RNG by hands Because it's a asactive server pages that i can't use rvest to crawl information.

And turn it into a csv and read it.

Website:https://lol.ggesports.com/zh-TW/Team/Matches?teamId=52

```{r}
data=read.csv('D:/SkySpiriT/NTU/107_DSCD/Project4(Does Karsa make RNG better)(LOL)/RNG.csv')
data
```

## Apirioi algorithm!

What's next?

I decide to use a ML algorithm to survey.

That's Apirioi algorithm!

It can find the relevance between things.

Let's take a look!

```{r}
library(arules)
library(arulesViz)
rule <- apriori(data,parameter=list(minlen=4, supp=0.1, conf=0.7),  
                appearance = list(default="lhs",rhs=c("result=Win", "result=Lose")))  
sort.rule <- sort(rule, by="lift")
```

There is another things to do .

Clean the rule.

Example:

Rule1:A & B play will win the game.

Rule2:A & B & C play will win the game.

Rule2 is more precise than rule1.

Why don't we delete rule1?
```{r}
subset.matrix <- as.matrix(is.subset(x=sort.rule, y=sort.rule))
subset.matrix[lower.tri(subset.matrix, diag=T)] <- NA
redundant <- colSums(subset.matrix, na.rm=T) >= 1
sort.rule <- sort.rule[!redundant]
```

## Result!
```{r}
inspect(sort.rule)
```

By the result,we can find that.

Karsa is a little bit better than Mlxg(by lift)

But,

there is another thing we can find.

When Karsa win the game,it is Able playing ADC most.(ADC is a another role Position in LOL)

But When Mlxg win the game,it is Uzi playing ADC most.

It show that Karsa and Mlxg also play an imprtant role in RNG.

So RNG fans,

let's not to fight for them, let's be fans of both of them! 
