---
title: "hw_4_Pratice API and Wordcloud with R"
author: "SkySpiriT"
date: "2018年5月1日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Use API to crawl

I have used 'rvest' package to crawl information before.

But this time,let's use different way to crawl !

API like a back door created by big company.

It is a easyier way to crawl,but it will let companies to trace your action.

## Facebook API

I decided to use Facebbok API for practicing.

And my target is:

let's find some secret of StarCraft2's facebook fan page!
```{r message=FALSE, warning=FALSE}
library(httr)
token = 'EAACEdEose0cBAEs19ju7PVNZBxKtCFUsZBGRDqrDpGPrL84c0c15EBHUsCcd34uAYz13k1gW8qz5Hv2p98xDjm8eGZBYGjwinen5S3qxLAK7dW3E8PXrdMSxZAHH48ImyzZBrlTpxyqt8PvwXyDacCIOILNVKUGcDwCZACZADvff1wZA33osnbaRez9PHCCICW7ZCZCApnBP5ZC9gZCzqzIYYJOY'
urlhead ='https://graph.facebook.com/v2.12/StarCraftZHTW/posts?fields=message&access_token='
url = paste0(urlhead,token)
res = httr::GET(url)
title = httr::content(res)
title=title$data
title=unlist(title)
title[1:5]
```

##  text cleaning & segment
After getting text of the post,there is a important thing we need to be do:text cleaning!

We have to clean the word we don't want to see(ex.Punctuation,Numbers,stopwords...)

After cleaning the word,we need to segment word and choose which part of speech we want.

```{r message=FALSE, warning=FALSE}
library(rJava)
library(tm) 
library(Rwordseg) 
library(tmcn) 
library(wordcloud) 
library(colorspace)
Data = Corpus(VectorSource(title))
Data = tm_map(Data ,stripWhitespace)
Data = tm_map(Data ,removePunctuation)
Data = tm_map(Data ,removeNumbers)
Data = tm_map(Data ,function(word){gsub("[A-Za-z0-9]","", word)})
stopward=stopwordsCN()
Data = tm_map(Data,removeWords,stopward)
Data=unlist(Data)
Wcloud = segmentCN(Data, nature = TRUE)
Wcloud = unlist( Wcloud )
noun = Wcloud[ names ( Wcloud ) == "n" ]
tab = table( noun )
Word = as.data.frame( tab[ tab >= 1 ] )
Word
```

## WordCloud!
The last step is :Creating my own wordcloud!

I trust everyone having the exprience that see the wordcloud create by FB and appear on their friend's wall.

But this time ,I tried to create my own wordcloud!
```{r message=FALSE, warning=FALSE}
wordcloud(words = Word$noun, freq = Word$Freq,min.freq =10,
  random.order = F, ordered.colors = T, scale=c(3,0.1),
  colors = rainbow_hcl( nrow( Word ) ))
```
