---
title: "Practice crawl with R"
author: "SkySpiriT(李季陽)"
date: "2018/3/14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Practice crawl with R

This our 2nd HW for DSCD.

We have to pratice crawl somthing on the NET with R.

First,We have to choose a Web to crawl.

I decided to choose starcraft bulletin in Bahamut forum for my firstweb to crawl.

It's my favorite forum because I'm a starcraft palyer.

## Let's do it !

I used rvest as my tool to crawl.

I want to search all title in first 3 pages of the forum.

Code & result
```{r , echo=TRUE}
library(xml2)
library(rvest)
library(magrittr)
result=c()
for(i in 1:3){
  sc.url=paste('https://forum.gamer.com.tw/B.php?page=',i,'&bsn=3037',sep='')
  title=read_html(sc.url) %>% html_nodes(".b-list__main") %>% html_text()
  title=gsub("\n", "", title)
  result[[i]]=title
}
unlist(result)

```

## Choose title which you want!
The crawl finished.

But I don't want to see something which I don't want to see.

Because I am Zerg player.

So I choose Zerg to search in first 10 pages of the forum.

Code & Result
```{r , echo=TRUE}
for(i in 1:10){
sc.url=paste('https://forum.gamer.com.tw/B.php?page=',i,'&bsn=3037',sep='')
  title=read_html(sc.url) %>% html_nodes(".b-list__main") %>% html_text()
  title=gsub("\n", "", title)
  title=title[grepl("蟲族",title)==TRUE ]
   result[[i]]=title
}
unlist(result)

```